\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
Word2Vec finished...Now GloVec

\subparagraph{Negative Sampling} This model has another name called \textbf{Noise Contrastive Estimation (NCE)}

>>>>

\subparagraph{Negative Sampling} This model has another name called \textbf{Noise Contrastive Estimation (NCE)}, and it was introduced by Gutmann and Hyvarinen.\\\\
NCE is roughly a maximum of log probability of the softmax that defines as follows:
log \sigma (x_{w_O}^{T} v_{w_I}) + \sum^{k}_{i = 1} \mathbb{E}_{w_i}~P_n(w) [log \sigma (-x_{w_O}^{T} v_{w_I}) ]
$P_n(w)$ is a noise distribution serving as a free parameter in the above formula. 
Mikolov has observed a number
of choices for Pn(w) and found that the unigram distribution U(w) raised to the 3/4rd power(i.e.,$U(w)^{3/4}/Z$) outperformed significantly the unigram and the uniform distributions.
\subsubsection{Results of Word2Vec}
  \includegraphics[scale=0.7]{word2vectorresult.png}
  \caption{Vector Space of Word2Vec}
Figure 10 shows that \textbf{Word2Vec} can be successful in creating the vector representation of a word, for example, \texttt{king} and \texttt{queen} has a closer Euclidean distance, and a smaller angle in-between.\\\\
Moreover, with vector representation of a word, we can write formula based off words. For instance: \\
\texttt{France + Paris - Being = China} \\
The result of \texttt{France + Paris - Being} would be equal or very close to the value of   \texttt{Beijing}. \\\\
Isn't that interesting?
\subsection{Global Vectors for Word Representation (GloVe)}
This model is highly similar to \textbf{Word2Vec} introduced above.

\subsection{ELMo}
\subsection{BERT}
\section{Question Answering}
